---
title: "Live Session2 Assignment"
author: "MSDS Data Science"
date: "January 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##  Question 1

#### 1. What is a basic workflow for reproducible research?
+ Data Gathering
+ Data Analysis
+ Presenting the results

#### 2. What are five practical tips for making research reproducible?
+ Document Everything
+ Record & Save them in files
+ Files, Comments, Literatrures must be Human Readable
+ Establish links/relationship between files 
+ Plan, Organize, store and make the files available.

#### 3. Give an example of how you might implement each tip.
>#####   Document Everything
+ Document every details from the begining of the research
+ Record the session / version info of the software(s) used for the research
+ List out the packages installed with dates and version number
+ System configurations (Mac/Windows/VM etc.,)
+ Any materials (books, research papers, Website) which provided assistance

>##### Record & Save them in files
+ Save all the details in a file which is easily accessible
+ Text files are the best, since it is free and OS independent
+ This helps even if the software is outdated in the future the code and  documentations can be used to reproduce in another language/tool

>##### Files, comments, literatures must be human readable
+ Make sure the comments, explanations are readable by human
+ Provide when the source was created, if there is any file/database access then small snippet on what is it about and why this is being accessed.
+ Make it a practice to add comments with great details, there is very good chance the independent researcher might not understand the code
+ Error & Exception handling

>##### Establish links/relationship between files
+ Create a relationship matrix of all the files and database
+ Publish a flow diagram, document the input & output where the details are orginating and how to recreate them

>##### Plan, Organize, store and make the files available
+ Develop a plan to organize and store the files and related materials 
+ Make sure they are readily available
+ Limit the amount of contend in the files to ease the navigation and reading

>#### 4. Which one of these do you think will be the most difficult?
+ I find the difficult part would be "Establish links/relationship between files".
+ This is a continuous effort, missing a small piece could derail the whole effort.

##  Question 2
```{r air_hist, echo=TRUE}
# We will be using the built-in dataset airquality which has daily air quality 
# measurements in New York from May to September 1973
str(airquality)

# Take only Temp columns
Temperature <- airquality$Temp
hist(Temperature)

# Histogram with added parameters
hist(Temperature,
     main="Maximum daily temperature at La Guardia Airport",
     xlab="Temperature in degrees Fahrenheit",
     xlim=c(50,100),
     col="darkmagenta",
     freq=FALSE)

# Q2A: Complete the following code to yield a scatterplot with x as Month and y as Temperature
# Make the x label "Month" and the y label "Temperature"
# Finally, make the title of the plot "Temperature by Month" 

plot(x=airquality$Month, y=airquality$Temp, xlab='Month', 
     ylab='Temperature', main = 'Temperature by Month')

# Q2B: Complete the following code to yield a scatter plot with x as Temperature and y as Ozone 
# Make the x label "Temperature" and the y label "Ozone",
# Make the title of the plot "Temperature vs Ozone"

plot(airquality$Temp ~ airquality$Ozone, xlab='Temperature',
     ylab='Ozone',main='Temperature vs Ozone')
```

##  Question 3
```{r cars}
summary(cars)
```

```{r cars_plot, echo=TRUE}
plot(cars)
```

```{r pressure_data}
summary(pressure)
```

```{r pressure_plot, echo=TRUE}
#3A, complete the following scatter plot. 
#The x axis is temperature, while the y axis is pressure
#Please title the graph "Temperature vs Pressure"

plot(temperature ~ pressure, data=pressure, main="Temperature vs Pressure", xlab='Temperature', ylab='Pressure')
```

```{r pressure_plot2, echo=TRUE}
#3B, complete the following scatter plot:
#x axis is pressure, y axis is temperature,
#Label the x axis as "Pressure" and the y axis as "Temperature"
#Title the graph as "Pressure vs Temperature"

plot (pressure ~ temperature, data=pressure, main="Pressure vs Temperature", xlab='Pressure', ylab='Temperature')
```
3C, This is written in R Markdown.